%% haunted-keep.tex
%
% A minimal example of how to use the rpg-module class. Replace the text of the
% module with your own adventure and compile with LaTeX!
%
% Lines which begin with '%' are comments, for explanatory purposes only. They
% are ignored by LaTeX and will not appear in the final document.



% First, tell LaTeX you want to format your document with the rpg-module class.
% We pass some options here: use US Letter paper size and use a serifed font.

\documentclass[letterpaper,serif]{rpg-module}

% You can add more packages here as required

\usepackage{parskip}                    % Don't indent paragraphs and add spacing between paragraphs

% The document text starts here

\begin{document}

% The title page is optional. If you want a title page, this is the minimum 
% amount of information required.

\title{The Haunted Keep}
\author{Tom Moldvay}
\maketitle

% Repeat the module title at the top of the first page

\showtitle

This is an example of the \LaTeX~rpg-module class, which shows how you might
format the example dungeon from p.B55--B60 of the D\&D Basic rulebook by Tom
Moldvay (1981).

% Part 1: Introduction. LaTeX takes care of formatting and numbering.

\part{Introduction}

% Put text to read out to the players inside the boxtext environment:

\begin{boxtext}
In the distant past, the Haunted Keep was the castle of the Rodemus family. It
was abandoned many years ago when the family mysteriously disappeared. It is
now rumored to be haunted. Strange lights and sounds are often seen and heard
in the ruins by passing townspeople.

Recently, a tribe of goblins has been raiding the countryside. On
their last raid they captured a dozen prisoners. The prisoners are all
relatives of the player characters, who have banded together to
rescue their relatives. The party has tracked the goblins to the Keep
or castle, right up to the only door to the east tower.

Most of the Haunted Keep is in ruins. Only two towers remain,
connected by a gatehouse, and only the first floors of these towers
are still intact. The Keep was built with rough granite blocks, now
pitted with age. The door into the east tower is wooden and one
hinge is rusted through.
\end{boxtext}

What the players do not know is that the Rodemus family has become
a family of wererats, and still live in tunnels under their old
castle. The family has joined the goblin raiders and are using them
to find the strengths of the surrounding countryside. If the raids
show the country folk to be weak, the family plans to raise a goblin
army and attack. The players will slowly discover this information,
little by little, as the adventure proceeds.

\part{The Gatehouse}

% Your document should be structured into parts, sections, subsections

\section*{DUNGEON KEY}

% Use subsections for rooms or locations in your adventure

\subsection{Bedroom}

This room appears to have once been a bedroom. It is filled with rotting, moldy
bedroom furniture, but is empty of monsters, treasure, and traps. The dust on
the floor has obviously been brushed to remove any footprints.

\subsection{Guard Post}

This room was once a guard post (when the Haunted Keep was a castle, before
becoming ruins). A faded, ragged tapestry showing a hunt divides the room in
half. Clinging to the side of the tapestry away from the characters (no
matter which door they use, unless they enter through both at
once) is a crab spider.

% Use the statblock macro to format monster stat blocks
% The format is \statblock{monster_name}{no_appearing}{hit_points}

\statblock{crab_spider}{1}{10}

On the north side of the tapestry is a wooden table and 3 wooden
chairs. A few moldy cards lie on the tabletop. Against the west wall
is a wooden chest. Any attempt to disturb the chest will bring an
immediate attack by the crab spider. The chest contains 99 sp
(silver pieces).

\subsection{Room of Faces}

The walls of this room are carved with leering human faces along their length.
A close examination of the north wall will reveal a crack around one particularly
sinister face. The face is on a swivel and can be pried open. Behind it is a
small iron safe cemented into the wall. The safe is trapped with
sleep gas which will billow out unless the trap is deactivated. The
sleep gas will fill a circular area 10' in diameter, but otherwise has
the same effects as a sleep spell; however, any creature who saves
vs. Poison will not be affected. Inside the safe are 400 sp and an
unmarked bottle of clear liquid (a potion of healing).

\subsection{Commander's Room}

This was the office of the tower commander, though all furnishings have been
removed. Two terrified prisoners huddle in one corner, their hands and feet in
chains. Guarding the prisoners are 4 hobgoblins who will fight anyone
who tries to rescue the prisoners.

\statblock{hobgoblin}{4}{7,9,4,5}

The largest hobgoblin has a locked iron box which contains 500 sp
and a jeweled necklace worth 1100 gp. Underneath a rug in the middle
of the floor is a trapdoor to the 2nd level.

\subsection{Chapel}

Once this room was a chapel, but now the altar is covered with dust. On the altar
is a grime-covered statuette depicting a muscular man with a rat's head. Most of
the twelve goblins are either sleeping on crude bunks along the walls or playing
dice games in a corner while two of them watch the door.

\statblock{goblin}{12}{5 each}

If loud noises are made in the corridor outside, all the goblins will be awake
when the party enters. They have no treasure.

\subsection{Empty Room}
% We put a cross-reference here from the next room
\label{empty_room}

It is difficult to determine what this room was used for. It is empty except for
a few splinters of wood, which may mean that the furniture was broken up (probably
to serve as firewood). The room is empty of monsters, treasure, and traps.

\subsection{Slime Room}

This room is similar to \ref{empty_room}, but there is a green slime clinging to the
ceiling. A cautious party will see the slime, but an unwary party will not see it
until it falls on one of them.

\statblock{green_slime}{1}{13}

\subsection{Guard Barracks}

This room was once a guard barracks. The floor has collapsed and the ceiling leaks.
The result is a 3' deep pool filled with scummy water. A partially waterlogged bunk
floats in the water. A rusted iron statue of a beautiful warrior maiden lies at the
bottom of the pool. The water is safe to walk through, and the statue is harmless
and worthless.

\subsection{Cubbyhole}

This cubbyhole has a secret door and was used to spy on those walking down the
corridor. There are now 4 goblins in the room, spying on anyone approaching in the
corridor. They have no treasure.

\statblock{goblin}{4}{5,3,4,1}

% Add some vertical space

\vspace{10ex}

% Table of Contents

\tableofcontents

% License information

\section{Open Game Content}
\label{ogl}

\begin{ogl}
\item System Reference Document, Copyright \copyright 2000--2003, Wizards of the Coast, Inc., by Jonathan Tweet, Monte Cook,
Skip Williams, Rich Baker, Andy Collins, David Noonan, Rich Redman, Bruce R. Cordell, John D. Rateliff, Thomas Reid, James
Wyatt, based on original material by E. Gary Gygax and Dave Arneson.
\end{ogl}

\end{document}
